Tables for PM2.5 Components Paper Manuscript

### 2021-06-25 code/data-viz/manuscript-tables.Rmd
IQRs

```{r Load data}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))

@@

@@

table.region <- dt.pmc %>% 
  group_by(Parameter, Region) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000)))

table.urban <- dt.pmc %>% 
  group_by(Parameter, Loc.Set) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  mutate(Region = Loc.Set,
         Region = factor(Region, levels = c("Urban", "Rural"))) %>% 
  select(-Loc.Set) %>% 
  arrange(Region)

@@

table <- dt.pmc %>% 
  group_by(Parameter) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  mutate(Region = "US",
         Region = factor(Region, levels = c("US"))) %>% 
  as.data.frame() %>% 
  add_row(table.region) %>% 
  add_row(table.urban) %>% 
  filter(Parameter != "EC") %>% 
  mutate(test = paste(Mean,"±",STD, sep = " ")) %>% 
  select(-Mean, -STD) %>% 
  pivot_wider(names_from = "Region",
              values_from = "test",
              names_sort = F) %>% 
  mutate(Parameter = factor(Parameter, levels = cmp)) %>% 
  arrange(Parameter) %>% 
  rename(Component = Parameter)

@@

### Table 3
```{r}
fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings <- rbind(fit$loadings) %>% as.data.frame()
factor.loadings <- rownames_to_column(factor.loadings, "Component")

colnames(factor.loadings) <- c("Component", "Soil", "Metals", "Traffic", 
                               "Biomass Combustion", "Coal combustion", "Salt", 
                               "Residual Oil Combustion", "Steel Industry") 
factor.loadings <- factor.loadings %>% 
  mutate_at(.vars = c("Soil", "Metals", "Traffic", "Biomass Combustion", 
                      "Coal combustion", "Salt", "Residual Oil Combustion", 
                      "Steel Industry"), ~sprintf('%.2f', .x))

@@

print(doc, target = here('output','table','main-tables.docx'))
```

### Figure 1 - Components SES
```{r}
doc <- read_docx()
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Table S2. Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Table S2. Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 2 - Factors SES
```{r}
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
                 cpt = "Table S3. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Table S3. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 3 - PM-Components Residual
```{r}
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
                 cpt = "Table S4. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
                 cpt = "Table S4. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 4 - PM-Factors Residual
```{r}
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
                 cpt = "Table S5. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
                 cpt = "Table S5. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S6. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S6. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S7. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S7. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S8. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S8. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S9. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S9. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S10. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S10. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S11. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S11. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
```

### Figure S3 - Components Urban
```{r}
doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure S4 - factors Urban
```{r}
doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.top.row,
                 cpt = "Table S14. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Table S14. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S15.  Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S15.  Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S16. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S16. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
                 cpt = "Table S17. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
                 cpt = "Table S17. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S18. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S18. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

>>>>

```{r Load data}
load(here('data','processed','pmc-daily.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))

@@

```{r - Parameter/Factor to Index}
### Components
Para.to.Index <- tribble(
  ~Index, ~Parameter,
   "As", "AS",
   "Ca", "CA",
   "Cu", "CU",
   "Cl", "CL",
   "Fe", "FE",
   "Pb", "PB",
   "Mn", "MN",
   "Ni", "NI",
   "Mg", "MG",
   "Se", "SE",
   "V", "V",
   "Si", "SI",
   "Zn", "ZN",
   "K", "K",
   "Na", "NA",
   "NO3", "NO3",
   "SO4", "SO4",
   "OC", "OC",
   "EC", "EC",
   "PM2.5", "PM"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))

### Factors 
Factor.to.Index <- tribble(
  ~Index, ~Parameter,
   "Soil", "Factor1",
   "Metals", "Factor2",
   "Traffic", "Factor3",
   "Biomass", "Factor4",
   "Coal", "Factor5",
   "Salt", "Factor6",
   "Oil", "Factor7",
   "Steel", "Factor8"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))
```

@@

table.region <- dt.pmc %>% 
   mutate(
    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
  group_by(Parameter, Region) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value)),
            STD = sprintf("%0.2f", sd(Value)))

table.urban <- dt.pmc %>% 
   mutate(
    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
  group_by(Parameter, Loc.Set) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value)),
            STD = sprintf("%0.2f", sd(Value))) %>% 
  mutate(Region = Loc.Set,
         Region = factor(Region, levels = c("Urban", "Rural"))) %>% 
  select(-Loc.Set) %>% 
  arrange(Region)

@@

table <- dt.pmc %>% 
   mutate(
    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
  group_by(Parameter) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value)),
            STD = sprintf("%0.2f", sd(Value))) %>% 
  mutate(Region = "US",
         Region = factor(Region, levels = c("US"))) %>% 
  as.data.frame() %>% 
  add_row(table.region) %>% 
  add_row(table.urban) %>% 
  filter(Parameter != "EC") %>% 
  mutate(test = paste(Mean,"±",STD, sep = " ")) %>% 
  select(-Mean, -STD) %>% 
  pivot_wider(names_from = "Region",
              values_from = "test",
              names_sort = F) %>% 
  mutate(Parameter = factor(Parameter, levels = cmp)) %>% 
  arrange(Parameter) %>% 
  merge(Para.to.Index) %>% 
  rename(Component = Index) %>% 
  select(Component, everything(), -Parameter)

@@

### Table 3
```{r}
fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings <- rbind(fit$loadings) %>% as.data.frame()
factor.loadings <- rownames_to_column(factor.loadings, "Parameter")

colnames(factor.loadings) <- c("Parameter", "Soil", "Metals", "Traffic", 
                               "Biomass Combustion", "Coal combustion", "Salt", 
                               "Residual Oil Combustion", "Steel Industry") 
factor.loadings <- factor.loadings %>% 
  mutate_at(.vars = c("Soil", "Metals", "Traffic", "Biomass Combustion", 
                      "Coal combustion", "Salt", "Residual Oil Combustion", 
                      "Steel Industry"), ~sprintf('%.2f', .x)) %>% 
  merge(Para.to.Index) %>% 
  rename(Component = Index) %>% 
  select(Component, everything(), -Parameter)

@@

print(doc, target = here('output','table','main-tables-2.docx'))
```

### Table S2
```{r}
cmp <- c("PM2.5", "Si", "Ca", "Pb", "Zn", "NO3", "OC", "K", "Cu", "Se", "SO4",
         "Na", "Cl", "Ni", "V", "Fe", "Mn")

### Components
pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.pmc.1yr) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(
    IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
    IQR = sprintf("%0.2f", IQR),
    Parameter = as.factor(Parameter)) %>% 
  merge(Para.to.Index) %>% 
  rename(Component = Index) %>% 
  select(Component, everything(), -Parameter) %>% 
  filter(Component %in% cmp) %>% 
  mutate(Component = factor(Component, levels = cmp)) %>% 
  arrange(Component) %>% 
  mutate(Source = ifelse(Component == "PM2.5", "PM2.5",
                         ifelse(Component %in% c("Si", "Ca"), "Soil",
                                ifelse(Component %in% c("Pb", "Zn"), "Metals",
                                       ifelse(Component %in% c("NO3", "OC"), "Traffic",
                         ifelse(Component %in% c("K", "Cu"), "Biomass",
                                ifelse(Component %in% c("Se", "SO4"), "Coal",
                                       ifelse(Component %in% c("Na", "Cl"), "Salt",
                         ifelse(Component %in% c("Ni", "V"), "Oil", "Steel")))))))))

### Factors excluding EC
fac.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.fac.1yr) %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR.2")%>% 
  mutate(IQR.2 = sprintf("%0.2f", IQR.2)) %>% 
  mutate(Parameter = as.factor(Parameter)) %>% 
  merge(Factor.to.Index) %>% 
  rename(Source = Index) %>% 
  select(Source, everything(), -Parameter)

table <- full_join(pmc.1yr.iqr, fac.1yr.iqr) %>% 
  select(Source, IQR.2, Component, IQR)

ft <- flextable(table)
ft <- merge_v(ft, j = c("Source", "IQR.2"))
ft <- theme_vanilla(ft)
ft <- vline(ft, j = c('IQR.2'))
ft <- padding(ft, padding = 0)
ft <- fontsize(ft, size = 10)
ft <- set_caption(ft, caption = "Table S2. IQR for 1-year moving average of source factors, PM2.5 and its components")
ft <- fontsize(ft, i = 1, size = 12, part = "header")
ft <- autofit(ft)

doc <- read_docx()
doc <- body_add_flextable(doc, value = ft, split = T)
doc <- body_add_par(doc, "a Source factors are unitless b Units are ng/m3 unless specified", style = "Normal")
body_add(doc, run_pagebreak())
```

### Figure 1 - Components SES
```{r}
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Table S3. Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Table S3. Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 2 - Factors SES
```{r}
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
                 cpt = "Table S4. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Table S4. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 3 - PM-Components Residual
```{r}
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
                 cpt = "Table S5. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
                 cpt = "Table S5. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure 4 - PM-Factors Residual
```{r}
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
                 cpt = "Table S6. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
                 cpt = "Table S6. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S7. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S7. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S8. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S8. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S9. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S9. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S10. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S10. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S11. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S11. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
```

### Figure S3 - Components Urban
```{r}
doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.top.row,
                 cpt = "Table S14. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = cmp.main, cuz = cuz.bot.row,
                 cpt = "Table S14. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

### Figure S4 - factors Urban
```{r}
doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.top.row,
                 cpt = "Table S15. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
                      select(-Loc.Set),
                    cmp = So.main, cuz = cuz.bot.row,
                 cpt = "Table S15. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S16.  Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S16.  Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
                 cpt = "Table S17. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
                 cpt = "Table S17. Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
                 cpt = "Table S18. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
                 cpt = "Table S18. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```

@@

doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
                 cpt = "Table S19. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ... Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
                 cpt = "Table S19. Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
```
